A Study of Immersion Factors Using an Augmented Reality Simulation

### 2009-06-25 trunk/Paper/paper.tex

By simulating augmented reality, we are freed from the current restrictions of tracking and display technology.  This simulated environment also affords easily controlled variables, and thus it may easily be reproduced.

@@

During each trial there are 20 people in addition to a virtual man \emph{Top Hat} wearing a tall black top hat walking an unpredictable path outside of the room.  The paths for each virtual person was randomly generated from set of coordinates exterior to the room.  Each path had the constraint that they must stay within the rectangular $50\times50$ $m^2$ area surrounding the room.  At each path point, the person will randomly change his/her walking speed within the range of 4 to 7 m/s.  \emph{Top Hat} had the additional constraints as follows.  He must start at the same location for each trial which made him visible by the participant through the front door the building.  In order to make the paths by of similar difficulty \emph{Tophat} must walk around the entire building at least once, and he must be visible through the windows for at least 10 seconds.  These constraints were met by randomly generating paths until all were satisfied.  We generated 27 sets of paths in this fashion, each corresponding to a specific trial.  We used a latin squares ordering to discourage the effects of learning.

@@

In our experiment we define performance as effectiveness in tracking \emph{Tophat}.  We measure performance by recording the angular distance (in yaw) between the the user's viewing direction and the direction towards the target character.  This measure ranges between zero and 180 degrees (we used the smaller of the two options, clockwise and counter-clockwise).  We record one measurement per video frame, at about sixty frames per second, resulting in about 3600 measurements for a one second trial.

>>>>

By simulating augmented reality, we are freed from the current restrictions of tracking and display technology.  This simulated environment also affords easily controlled variables, and thus the experiment may be replicated.

@@

During each trial there are 20 people in addition to a virtual man \emph{Top Hat} wearing a tall black top hat walking an unpredictable path outside of the room.  The paths for each virtual person was randomly generated from set of coordinates exterior to the room.  Each path had the constraint that they must stay within the rectangular $50\times50$ $m^2$ area surrounding the room.  At each path point, the person will randomly change his/her walking speed within the range of 4 to 7 m/s.  Top Hat had the additional constraints as follows.  He must start at the same location for each trial which made him visible by the participant through the front door the building.  In order to make the paths by of similar difficulty Top Hat must walk around the entire building at least once, and he must be visible through the windows for at least 10 seconds.  These constraints were met by randomly generating paths until all were satisfied.  We generated 27 sets of paths in this fashion, each corresponding to a specific trial.  We used a latin squares ordering to discourage the effects of learning.

@@

In our experiment we define performance as effectiveness in tracking Top Hat.  We measure performance by recording the angular distance (in yaw) between the the user's viewing direction and the direction towards the target character.  This measure ranges between zero and 180 degrees (we used the smaller of the two options, clockwise and counter-clockwise).  We record one measurement per video frame, at about sixty frames per second, resulting in about 3600 measurements for a one second trial.
